Studying the Performance of the Jellyfish Optimiser for the Application of Projection Pursuit

### 2024-05-28 optim.qmd
Update optim.qmd

From the literature, it is commonly understood that a large squint angle
implies that the function is easy to optimize, because we do not need to
be very close to the perfect view to see the structure. A small squint
angle means that the derivative of the index function can still be very
large values near the optimal point and will rapidly change as we get
even closer to the optimum. As such we can observe the second order
gradient, which is the rate of change of gradient, over the space we are
searching. For some index functions, the second order gradient is not
well-defined, we can approximate the second order gradient vector in
similar fashion as the above section.

>>>>

From the literature, it is commonly understood that a large squint angle
implies that the objective function value is close to optimal even when we are not very close to the perfect view to see the structure. A small squint angle means that index function value improves substantially only when we are very close to the perfect view. As such, low squintability implies rapid improvement in the index value when near the perfect view.

In this study, we propose two metrics to capture the notion of squintability.

[We generate random points that is beyond 1.5 projection distance and interpolate. Then we fit a kernel or use nonlinear least squares.]

First, parametric model.

[Nicolas's pdf]

Second, we consider the product of the largest absolute magnitude of rate of change of $f$ and the corresponding projection angle as a second measure of squintability. Since $f$ is decreasing, the rate of change of $f$ is negative and thus \[|\underset{x}{\min} f('x)|\] gives the absolute magnitude of the most negative rate of change.

[Nicolas's pdf]
